Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-07-09 manuscript/04-results.Rmd
Update 04-results.Rmd

### droughts(?)
[description of the 3 droughts in terms of timing, duration, severity, proportion of trees showing pointer year..?]

>>>>

### droughts(?)
[description of the 3 droughts in terms of timing, duration, severity, proportion of trees showing pointer year..?. See [Slette et al. (2019)](https://onlinelibrary-wiley-com.smithsonian.idm.oclc.org/doi/abs/10.1111/gcb.14747)]
